\documentclass{article}
\usepackage[utf8]{inputenc}

\title{\textbf{RIGHT NOW THIS IS A COPY OF THE OUTLINE}
Monitoring Parsl Work Flows}
\author{Connor Pigg and Dr. Daniel Katz}
\date{July 2018}

\usepackage{natbib}
\usepackage{graphicx}

\begin{document}

\maketitle

\section{Abstract}
\input{abstract.tex}
\pagebreak

\section{Introduction}
\input{intro.tex}

\section{Project Goals}
The purpose of my project is to provide users with the ability to monitor the behavior of their work flows.
The plan is to create a software solution built using the project's existing tools and/or additional libraries.
Ideally, the monitoring should provide an abundance of information about the behavior of execution in a clear visual format.
Specifically, the outline of my research is as follows.
I will familiarize myself with the project and its team to understand the context and resources that my solution should harmonize with.
I will explore available additional resources and tools I find or are recommended such as Kibana, Elasticsearch, and psutil.
Next, I will begin prototyping and iteratively build a solution that incrementally adds features to monitoring.
Finally, I will assess the solution and prepare a finalized version of the work for the completion of the project.

\section{Background and Significance}
Work flow software is used by researchers and projects to automate the transition between actions that typically occur in any given process.
Parsl empowers users to utilize the parallel capabilities of computers through implicit parallelization of these work flows.
This speeds up the process and reduces human errors in the process.
These tools also give users the ability to audit, publish, and debug their work flows improving the quality and reproducability of a process.
To further enable these specific uses of work flow tools, this project will add monitoring to Parsl.

Parsl's decision to include monitoring at such a relatively young age conveys the importance of monitoring to users of such software.

\section{Potential Benefits}
These monitoring capabilities will improve the user's understanding of the behavior of their work flow.
This allows the detection of abnormalities, errors, and performance of their work flow.
This information improves the efficiency at which a user can solve work flow problems and achieve results.

Monitoring should also increase adoption of automated work flows.
Increased adoption would improve the productivity of these users and empower these users to contribute more to their communities.

\section{Conclusion}
Parsl is a useful tool for creating, managing, and soon to be monitoring scientific work flows.
This project will improve Parsl and empower its users as it begins to satisfy the need to observe the behavior of their applications.

I will go through the design process for computational research tools and build a solution for monitoring.
This project will empower the project with monitoring features and me with a greater knowledge of research work flows and the development process.

\bibliographystyle{plain}
\bibliography{references}
\end{document}
